# This is prep_chl.Rmd

This is for modifying the existing chl repo with new regions (16 total, up from original 12). Should have been able to run edit_repos.rmd but needed to make some additional tweaks to the shapefiles. 

## 0. add shp to `sc_studies_custom.csv` 

Add by hand to `ohi-webapps/custom/sc_studies_custom.csv`

## 1. setup

```{r setup, eval=F}

source('~/github/ohi-webapps/_source_and_load.r')

key <- 'chl'

# directories
setwd(dir_webapps)
dir_spatial = file.path(dir_M, 'git-annex/clip-n-ship', key, 'spatial')
dir_shp_in  = file.path(dir_spatial, 'custom')

source(file.path(dir_webapps, 'create_init.R'))
source(file.path(dir_webapps, 'create_init_sc.R'))


```

## Inspect user's shapefiles and save as OHI shapefiles

```{r inspect shapefiles, eval=F}

# read in shp files and save with desired headers in data frame.
shp = rgdal::readOGR(dsn = file.path(dir_shp_in, 'raw'),
              layer = 'Chile_Ocean_Regions')

# view dataframe and map
shp@data
shp
plot(shp)

# save as shapefiles. will create 4 files: .dbf, .prj, .shp, .shx
writeOGR(shp, dsn = dir_shp_in, 
         layer = 'chl_shp', driver = 'ESRI Shapefile', overwrite=T) 

## save rgn_offshore_data.csv on git-annex
readr::write_csv(shp@data %>% 
                   select(rgn_id, rgn_name, area_km2) %>%
                   arrange(rgn_id), 
                 file.path(dir_spatial, 'rgn_offshore_data.csv'))

# save lookup table with unique rgn_ids on github
readr::write_csv(shp@data, sprintf('~/github/ohi-webapps/custom/%s/rgns_custom.csv', key))

```
looking good. 

## Clone existing repo

```{r clone existing repo, eval=FALSE}

## clone chl repo
unlink(dir_repo, recursive=T, force=T)
repo <- clone(git_url, normalizePath(dir_repo, mustWork=F))
setwd(dir_repo)

```

## Unpopulate existing layers; rename scenario
delete contents so can start afresh
```{r}
## rename subcountry2014 -> region2016. 
file.rename(from = file.path(dir_repo, 'subcountry2014'),
            to   = file.path(dir_repo, 'region2016'))

## unpopulate_layers_conf
unpopulate_layers_conf(key, dir_repos, dir_repo, git_url, default_scenario)

## a few extra files to delete from CHL: 
also_delete <- paste(dir_repo, c('copy_webapps_templates.r', 'ohi-travis-functions.R', 'travis-tool.sh'), sep = '/')
unlink(also_delete, recursive = TRUE, force = TRUE)

```

## Repopulate all the things

```{r}

## populate layers folder and layers.csv, and conf. Doesn't push. 
populate_layers(key, dir_repo, lyrs_gl, dir_global, dir_scenario, multi_nation = FALSE)
populate_conf(key, dir_scenario, dir_global) ## look at TODOs in functions.r
populate_etc(key, dir_scenario)

##TODO: check calculate_scores.r runs 

## TODO: now call map functions from below

```


## Push!

```{r}
## push draft branch
source('~/github/ohi-webapps/ohi-functions.R')          # TODO: move these to R folder as separate .r functions
setwd(dir_repo)
push_branch('draft') # source('ohi-functions.r')
system('git pull')

```



## Create Repo's Maps

```{r create_repo_map etc}
# create_repo_map
create_repo_map(key, dir_shp_in, dir_spatial) 

```
