# This is edit_repos.Rmd

Note: This is a companion file to `edit_webapps.rmd` in the ohi-webapps@master branch. 

# Update existing repos with new ohicore resilience structure
July, 2016

Written while also updating create_all.r and trying to move towards a package. 

- col X
- ohibc
- arc X
- chl x
- cdz
- rdv x

```{r}

## run setup from create_all

## set key
key <- 'ohi-northeast'

# set vars by subcountry key
source('create_init.R')   
knitr::opts_knit$set(root.dir = dir_repos)
source(sprintf('%s/ohi-webapps/create_init_sc.R', dir_github))    

## clone repo and remotes
ohirepos::clone_repo(dir_repos, dir_repo, git_url)

## unpopulate layers, conf, etc. Doesn't push. 
ohirepos::unpopulate_layers_conf(key, dir_repos, dir_repo, git_url, default_scenario)

## set wd to scenario folder
dir_scenario = file.path(dir_repo, basename(default_branch_scenario))
if (!exists(dir_scenario)) dir.create(dir_scenario)
knitr::opts_knit$set(root.dir = dir_scenario)

## populate layers folder and layers.csv, and conf. Doesn't push. 
ohirepos::populate_layers(key, dir_repo, lyrs_gl, dir_global, default_scenario, multi_nation=FALSE)
populate_conf()
populate_etc()

## push draft branch
source('~/github/ohi-webapps/ohi-functions.R')          
setwd(dir_repo)
push_branch('draft') # source('ohi-functions.r')
system('git pull')

```


# Create prep repo

## 0. add info to `sc_studies_custom.csv` 

Add by hand to `ohi-webapps/custom/sc_studies_custom.csv`

## 1. set key

```{r key}
## 1. set key
key <- 'rdv'

```

## 2. Set directories etc

```{r create prep repo}
## setup ----
source('~/github/ohi-webapps/_source_and_load.r')
setwd(dir_webapps)
source(file.path(dir_webapps, 'create_init.R'))
source(file.path(dir_webapps, 'create_init_sc.R'))
```

## 3. Create prep repo

```{r}
## create github repo on github.com
create_gh_repo(key, gh_token, github_user)

## set working dir
dir.create(dir_repo)

## add readme and prep folder
populate_init(key)
populate_prep(key)
```


## 4. Inspect Custom Shapefiles

For now, in prep_rdv.rmd


## 5. Populate all the things

```{r}

## create scenario folder
dir.create(dir_scenario, showWarning=FALSE)

## populate layers folder and layers.csv, and conf. Doesn't push. 
ohirepos::populate_layers(key, dir_repo, lyrs_gl, dir_global, dir_scenario, multi_nation = FALSE)
populate_conf(key, dir_scenario, dir_global) ## look at TODOs in functions.r, eg had to remove ICO gapfilling for NE
populate_etc(key, dir_scenario)

##TODO: check calculate_scores.r runs 
# - [ ] look into pressures, resilience matrix stuff  <<-- do this next

# create_repo_map
source('~/github/ohirepos/R/create_repo_map') ## build package and delete
create_repo_map(key, dir_spatial, dir_scenario) 

```

## Push!

```{r}
## push master branch   # TODO: move ohi-functions.R fxns to R folder as separate .r functions
setwd(dir_repo)
push_branch('master', sprintf('populate full %s repo', key)) # ohirepos::
system('git pull')

```




