# This is edit_repos.Rmd

Note: This is a companion file to `edit_webapps.rmd` in the ohi-webapps@master branch. 

# Update existing repos with new ohicore resilience structure
July, 2016

Written while also updating create_all.r and trying to move towards a package. 

- col X
- ohibc
- arc X
- chl
- cdz


```{r}

## run setup from create_all

## set key
key <- 'chl'

# set vars by subcountry key
source('create_init.R')   
setwd(dir_repos)
source(sprintf('%s/ohi-webapps/create_init_sc.R', dir_github))    

## clone repo and remotes
clone_repo(dir_repos, dir_repo, git_url)

## unpopulate layers, conf, etc. Doesn't push. 
unpopulate_layers_conf(key, dir_repos, dir_repo, git_url, default_scenario)

## set wd to scenario folder
dir_scenario = file.path(dir_repo, basename(default_branch_scenario))
setwd(dir_scenario)

## populate layers folder and layers.csv, and conf. Doesn't push. 
populate_layers(key, dir_repo, lyrs_gl, default_scenario, sfx_global, multi_nation=FALSE)
populate_conf()
populate_etc()

## push draft branch
source('~/github/ohi-webapps/ohi-functions.R')          # TODO: move these to R folder as separate .r functions
setwd(dir_repo)
push_branch('draft') # source('ohi-functions.r')
system('git pull')


```


# Create prep repo

## 0. add info to `sc_studies_custom.csv` 

Add by hand to `ohi-webapps/custom/sc_studies_custom.csv`

## 1. set key

```{r key}
## 1. set key
key <- 'mhi'

```

## 2. Create prep repo

```{r create prep repo}
## setup ----
source('~/github/ohi-webapps/_source_and_load.r')
setwd(dir_webapps)
source(file.path(dir_webapps, 'create_init.R'))
source(file.path(dir_webapps, 'create_init_sc.R'))

## create github repo on github.com
create_gh_repo(key, gh_token, github_user)

## set working dir
dir.create(dir_repo)

## add readme and prep folder
populate_init(key)
populate_prep(key)

```


