# This is edit_webapps.Rmd

Note: this file (`edit_webapps.rmd`) was previously called `edit_webapps.r`.

This file accompanies the `ohi-webapp` repo's `create_all.r` and `create_functions.r` to modify exisiting webapps or to create custom webapps. All the code chunks are set to `eval=F` so that they are not run when the `.rmd` file is rendered. This serves mainly as a record of modifications or processes that were done to update the webapps. Run individual lines within the chunks or add new ones as needed. 

## setup

```{r setup, eval=F}

# set vars and get functions
setwd('~/github/ohi-webapps')
source('create_init.R')
source('create_functions.R')

```

## Update WebApps (gh-pages)
2015-Jan, 2015-May by bbest, jules32 

1. make any changes you want to the files in `gh-pages`; ex: `ohi-webapps/gh-pages/about/index.md`
2. run the following chunk:

```{r update webapps, eval=F}

keys = sc_studies %>% filter(!is.na(sc_annex_dir)) %>% select(sc_key)
keys = keys[,1]
sapply(keys, update_website, 'update About using ohi-webapps/create_functions.R - update_website()')

# TODO: fix update_draft function to copy functions.R and update layers.csv descriptions.
#sapply(keys, update_draft, 'update About using ohi-webapps/create_functions.R - update_draft()') 

```

## Move Apps to NCEAS server
2015-March. One-time only

1. change app_url to https://ohi-science.nceas.ucsb.edu/ (from https://ohi-science.shinyapps.io) in 2 files: 
  - `ohi-webapps/gh-pages/_config.brew.yml`
  - `ohi-webapps/app.brew.yml`
2. run the following chunk:

```{r move apps to NCEAS server, eval=F}

keys = sc_studies %>% filter(!is.na(sc_annex_dir)) %>% select(sc_key)
keys = keys[,1] # keys = 'blz'
# sapply(keys[1:3], revert_website, '2015-03-23 08:00:00') # done 2015-03-24 by bbest, jules32
sapply(keys, deploy_app_nceas)

# restart R and run above before line below
sapply(keys, update_website,   'move Shiny App onto NCEAS server - update_website()')

```


## fixing GYE 
2015-03-25 

```{r fixing GYE, eval=F}

revert_website('gye', '2015-03-23 08:00:00')
update_website('gye', 'move Shiny App onto NCEAS server - update_website()')
deploy_app_nceas('gye', nceas_user='bbest')

```


## create ohi-global

```{r create ohi-global, eval=F}

key = 'ohi-global'
update_website(key, msg='update _config.yml branch_scenario, ohi-webapps/create_functions.R - update_website()')
deploy_app_nceas(key)

```

## Updates to app branch; additions to draft branch
2015-May

```{r updates to app branch + additions to draft branch, eval=F}

keys = sc_studies %>% filter(!is.na(sc_annex_dir)) %>% select(sc_key) %>% 
  filter(!sc_key %in% c('gye', 'bhi', 'chn', 'aia', 'tto', 'asm', 'civ'))
keys = keys[,1] # keys = keys[1:10,1]
sapply(keys, additions_draft, msg='update travis.yml + additions, ohi-webapps/create_functions.R - additions_draft()')
sapply(keys, update_website, msg='update _config.yml branch_scenario, ohi-webapps/create_functions.R - update_website()')

# `jstewart@fitz:/srv/shiny-server$ sudo service shiny-server restart` restart fitz server in terminal

sapply(keys, deploy_app_nceas)
```

## Create `webapp_yml_secure_recip.csv`
2015-May-20

One-time only. `webapp_yml_secure_recip.csv` is a list of which repos have secure/recipient problems

```{r create webapp_yml_secure_recip.csv, eval=F}

# csv_status=file.path(dir_github, 'ohi-webapps/tmp/webapp_yml_secure_recip.csv')
# for (dir in list.dirs(dir_repos, recursive=F)){ # dir = '/Users/jstewart/github/clip-n-ship/cog'
#  
#   key = str_split_fixed(dir, '/', 6)[6]
#   key <<- key
#   source(file.path(dir_github, 'ohi-webapps/create_init_sc.R'))
#   
#   # switch to draft branch and get latest
#   system('git checkout draft; git pull')
#   
#   yml = file.path(dir, '.travis.yml')
#   
#   if ( file.exists(yml) ){
#     y = yaml.load_file(yml)
#   
#     # check #1: has secure var?
#     secure = 'secure' %in% names(unlist(y$env$global))
#     
#     # check #2: has lowndes as a recipient # TODO: switch to ohi-science@nceas.ucsb.edu?
#     recip = 'lowndes@nceas.ucsb.edu' %in% unlist(y$notifications$email$recipients)
#     
#     # add to csv_status log
#     read.csv(csv_status, stringsAsFactors=F, na.strings='') %>%
#       filter(sc_key != key) %>%
#       rbind(
#         data.frame(
#           sc_key = key,
#           travis_secure = secure,
#           travis_recip  = recip,
#           travis_status = '',
#           date_checked  = as.character(Sys.time()))) %>%
#       write.csv(csv_status, row.names=F, na='')    
#   }
# }

```

## Update .travis.yml with env:global:secure variable w/ encrypted string that sets GH_TOKEN
2015-May with @bbest. 

We want to compare current travis status to the original status in Nov2014 so that we only focus on repos that have since broken.

```{r update .travis.yml, eval=F}

# 1. access travis status from November 2014
keys_2014_11_28 = readr::read_csv(
  'https://raw.githubusercontent.com/OHI-Science/ohi-webapps/9c7a3f152ba10000b7ad7380de1d7d13eb486898/tmp/webapp_travis_status.csv', 
  col_types = 'cc_') # don't need to read in date column, see github.com/hadley/readr

# 2. check and save the current travis status (don't use status_travis() because that will enable travis, we just want to check)
sapply(keys_2014_11_28$sc_key, status_travis_check) # this logs in 'webapp_travis_status_check.csv'
keys_2015_05_21 = read.csv('~/github/ohi-webapps/tmp/webapp_travis_status_check.csv')

# 3. compare keys that that originally were passing; now aren't. JSL COME BACK HERE
keys = keys_2014_11_28 %>%
  select(sc_key, status_orig = travis_status) %>%
  full_join(keys_2015_05_21 %>%
              select(sc_key, status_now = travis_status), 
            by= 'sc_key') %>%
  filter(status_orig == 'passed' & status_now != 'passed', 
         !sc_key %in% c('chn', 'dji'))

# sapply(keys, additions_draft, msg='update travis.yml + additions, ohi-webapps/create_functions.R - additions_draft()')
# sapply(keys, update_website, msg='update _config.yml branch_scenario, ohi-webapps/create_functions.R - update_website()')
sapply(keys, fix_travis_yml)
sapply(keys$sc_key, status_travis_check) # this logs in 'webapp_travis_status_check.csv'
sapply(keys, deploy_app_nceas)
#khm rsync error

```

## fix CHN scenario issue
2015-May-22
published branch still reads 'subcountry2014' not 'province2015'. Fix this; merge branches.


```{r fix CHN scenario, eval=F}
# additions_draft('chn')
# deploy_app_nceas('chn')

```

## update_webapp_notravis() 
2015-July

For in-progress repos, 

```{r update_webapp_notravis, eval=F}

keys = c('chn', 'per', 'bhi', 'chl', 'esp', 'jpn', 'kor') # 'gye' also done, but with merge_pub=T
sapply(keys, update_webapp_notravis, run_calc_scores=F, merge_pub=F)
sapply(keys, deploy_app_nceas)

# 2015 Sept
keys = 'gye'
sapply(keys, update_webapp_notravis, run_calc_scores=F, merge_pub=T)
sapply(keys, deploy_app_nceas)

```

## additions_draft() brew copy_webapps_templates.r for gye and chn
2015-July-7 

One time only. In this case I just ran Step 6 of `create_functions.r - additions_draft()`

```{r additions_draft for gye+chn, eval=F}

additions_draft(key='chn', msg='ohi-webapps/create_functions.R - additions_draft()')

```

## redo bhi repo+webapp with new regions

Rough workflow: 

- receive Baltic spatial files with region boundaries
- identify Baltic countries 
- create repo for bhi as a whole
- create Baltic layers by binding layers for each Baltic country's repo
- populate bhi repo with layers and maps
- push to bhi repo branches, including webapp

```{r redo bhi repo+webapp, eval=F}

# see ohi-webapps/custom/bhi/prep_bhi.rmd

```


## create arctic repo+webapp

Arctic nations: USA, Canada, Russia, Norway and Denmark/Greenland

This workflow will differ from previous approaches because the Arctic is a subset of ohi-global; regions are whole nations (as in ohi-global). This is going to be the simplest case I've done so far (I think). I might be able to just: 

- create arc repo
- combine info from these repos: rus, usa, can, nor, grl (as in Step 7 of `prep_bhi.rmd`)
- create the maps (see [github.com/OHI-Science/issues/issues/516]())

For reference, previous custom approaches:
- The Baltic (bhi) is a subset of ohi-global but with sub-regions identified first and created as temporary repos and regions ended up being an intersection of eez x basin
- Gulf of Guayaquil (gye) was essentially a normal webapp creation, but with custom boundaries.

Rough workflow: 

- Add entry for arc in `ohi-webapps/custom/sc_studies_custom/csv`
- create repo named arc (fyi `create_functions.r - rename_gh_repo` exists too if I need it)
- make maps
- instead of `populate_draft_branch()`, combine relevant regions from existing 5 repos for arctic countries
- continue with `create_all.r`
- don't add travis stuff; add it fitz's `/srv/shiny-server/_update_apps.bash`, see [github.com/OHI-Science/issues/issues/512]()

```{r create arctic repo and webapp, eval=F}

# set vars by key
key = 'arc'

setwd(dir_repos)
source(sprintf('%s/ohi-webapps/create_init_sc.R', dir_github))
setwd(dir_repo)
  
##order of functions to run from create_all.r: 

# create repo on github.com
repo = create_gh_repo(key) 

# make maps
# ohi-webapps/custom/arc/prep_arc.rmd  # prep maps ## in progress!
# custom_maps()

# instead of `populate_draft_branch`, copy all contents from ohi-global repo, filter only arctic countries
subset_global.r # need to create this!
# 

```

## populate OHIBC repo and create webapp

The repo already exists: https://github.com/OHI-Science/ohibc

Rough workflow:

- Add entry for ohibc in `ohi-webapps/custom/sc_studies_custom/csv`
- `populate_draft_branch()`
- continue with `create_all.r`
- don't add travis stuff; add it fitz's `/srv/shiny-server/_update_apps.bash`, see [github.com/OHI-Science/issues/issues/512]()

```{r populate ohibc repo and webapp, eval=F}

# set vars by key
key = 'ohibc'

setwd(dir_repos)
source(sprintf('%s/ohi-webapps/create_init_sc.R', dir_github))
setwd(dir_repo)
  
##order of functions to run from create_all.r: 

# create repo on github.com
repo = create_gh_repo(key) 

# make maps
# ohi-webapps/custom/ohibc/prep_ohibc.rmd  # prep maps ## in progress!
# custom_maps()

# instead of `populate_draft_branch`, copy all contents from ohi-global repo, filter only arctic countries
subset_global.r # need to create this!
# 

```

## compare OHI+ scores to global scores

the color-coded .html file produced is by @Melsteroni and @oharac in [Reporting.Rmd](https://github.com/OHI-Science/ohi-global/blob/f53f4b55e6809433c4c62317115642bc57be4fac/global2015/Reporting/Reporting.Rmd#difference-between-old-and-new-scores-using-2013-benchmark)

So far I've only run this for `ohi-israel`


```{r compare ohiplus_global, eval=F}

# set vars by key
keys = 'ohi-israel' # 'gye'

for (key in keys){ # key = 'gye'
  
  setwd(dir_repos)
  source(sprintf('%s/ohi-webapps/create_init_sc.R', dir_github))
  
  # brew .R template and README
  brew(sprintf('%s/ohi-webapps/compare_scores_global_OHIplus.brew.R', dir_github),
       '~/github/ohi-israel/med2014/reports/compare_scores_global_OHIplus.R')
  brew(sprintf('%s/ohi-webapps/README_compare_scores_global_OHIplus.brew.md', dir_github),
       '~/github/ohi-israel/med2014/reports/README.md')
}


```
