---
title: "Startup Instructions"
output:
  pdf_document:
    number_sections: T
    toc: T
    toc_depth: 3
  md_document:
    variant: markdown_github
---

```{r, eval=TRUE, message = FALSE, echo=FALSE}

library(devtools)
library(dplyr)
library(ggplot2)
library(stringr)
library(reshape2)
suppressWarnings(library(ohicore))

```

# Introduction

Welcome to !repo.  

!repo is repository: a folder of files and scripts required to run the Ocean Health Index (OHI) Toolbox and will be necessary to complete your regional assessment. Although the Toolbox is used to calculate Index scores after all data have been gathered and decisions have been made, it is important to understand the structure of the Toolbox file system, as this aids in bookkeeping, which is important for transparent and reproducible science.  

Please refer to the **Ocean Health Index Toolbox Manual** for instructions on how to prepare to use the Toolbox, including how to download this repository using GitHub to facilitate collaboration. 

# !repo has been extracted from the global repository

This repository is a starting point for your assessment. Information for !study_area has been extracted from the global assessment and will serve as a template to modify to better represent the local charactistics of !study_area. This is to say that all data within this repository are based on global databases where !study_area is represented at the national scale.

With !repo, you will calculate scores for each region within !study_area and combine them into a single score for !study_area. You will be able to substitute much of the global data provided with locally-available data and indicators, and you will be able to modify the goal models to better reflect local data and priorities. This will provide a finer-scale understanding of ocean health in !study_area.  

## `!x` regions within !study_area

Whereas in the global assessments, !study_area was one region combined within the study area (the entire world), here, !study_area is the study area, which contains `!x` subcountry coastal regions: `!listed_here`.  

These regions were identified by Global Administrative Areas (www.gadm.org) as being the largest subcountry unit within !study_area. The boundaries of these regions have been extended offshore to divide the exclusive economic zone (EEZ) of !study_area into portions for each subcountry region. These regions have been provided because in previously completed regional assessment, this is often the scale at which data are available and policy decisions are made. However, it is possible to use different regions than the ones provided here. See [ohi-science.org/pages/create_regions.html](http://ohi-science.org/pages/create_regions.html) for more details.  

You are able to view the regions within !study_area, from GitHub by going to: [github.com/OHI-Science/!repo/blob/master/subcountry2014/spatial/regions_gcs.geojson](https://github.com/OHI-Science/!repo/blob/master/subcountry2014/spatial/regions_gcs.geojson).

# File System

Within the !repo repository is **subcountry2014**, the scenario folder. This contains all the data, functions and other files required to calculate the OHI scores for the `!x` regions within !study_area. You will modify the files within this folder to complete your assessment. 

## Data

All data used to calculate OHI scores are contained within the `layers` folder, and the `layers.csv` file acts as a registry for managing all data. In most cases, data provided within the `layers` folder are only place-holders and should be replaced by local, finer-resolution data for your assessment.  

Values within the *.csv* files are based on values for all of !study_area and if data are available locally by region, this will allow for a much more precise assessment of ocean health in !study_area. Any data layers that did not have available values for !study_area have place-holder values based on the global mean and are listed in `layers-empty_swapping-global-mean.csv`.

### *layers.csv*

`layers.csv` is the registry that manages all data to be used in your assessment.

Each row in this file represents a specific data layer that has been prepared and formatted properly for the Toolbox. The first columns contain information inputted by the user; other columns are generated later by the Toolbox App as it confirms data formatting and content. The first columns have the following information:

 + ***targets*** indicates how the data layer related goals or dimensions. Goals are indicated with two-letter codes and sub-goals are indicated with three-letter codes, with pressures, resilience, and spatial layers indicated separately.
 
```{r, results='asis', echo=F}
knitr::kable(
  read.csv('~/github/ohi-global/eez2014/conf/goals.csv') %>%
    select(goal, name))
```
 
 + ***layer*** is the identifying name of the data layer, which will be used in R scripts like `functions.R` and *.csv* files like `pressures_matrix.csv` and `resilience_matrix.csv`. This is also displayed on the Toolbox App under the drop-down menu when the variable type is ‘input layer’.
 + ***name*** is a longer title of the data layer; this is displayed on the Toolbox App under the drop-down menu when the variable type is ‘input layer’.
 + ***description*** is further description of the data layer; this is also displayed on the Toolbox App under the drop-down menu when the variable type is ‘input layer’.
 + ***fld_value*** indicates the units along with the units column.
 + ***units*** some clarification about the unit of measure in which the data are reported
 + ***filename*** is the *.csv* filename that holds the data layer information, and is located in the folder ‘layers’.
 
 
### *layers* folder
The `layers` folder contains every data layer as an individual comma separated value (*.csv*) file. The names of the *.csv* files within the layers folder correspond to those listed in the *filename* column of the `layers.csv` file described above. *.csv* files can be opened with text editor software, or will open by default by Microsoft Excel or similar software.

Open any *.csv* file within `layers` and note two important things:

1. There are `!x` numbers represented within the data file: these are unique region identifiers *rgn_id*s for each coastal region in !study_area. The layer called `rgn_layers.csv` identifies which *rgn_id* is associated with which number.
2. There is a specific format that the Toolbox expects and requires that every *.csv* file within the `layers` folder has. Note the unique region identifier (*rgn_id*) with a single associated *score* or *value*, and that the data are presented in ‘long format’ with minimal columns. See the *Formatting Data for the Toolbox* section of the OHI-Manual for more details.


### notes on georegionally-gapfilled data

```{r, results='asis', echo=F}

# georegion list
g = read.csv('~/github/ohi-global/eez2014/layers/rgn_georegions.csv') %>%
  filter(level == 'r2') %>%
  inner_join(
      read.csv(file.path('~/github/ohi-global/eez2013/layers/rgn_labels.csv')) %>%
        select(rgn_id, rgn_nam=label),
    by='rgn_id') %>%
  select(rgn_id, rgn_nam, georgn_id) 

# identify study area. !hardcoded for now !study_area
ra = 'Colombia'

# identify study area's georegion
g_ra = g %>%
  filter(rgn_nam == ra)

# identify other rgns within georegion
g_rgns = g %>%
  filter(georgn_id == g_ra$georgn_id, 
         rgn_nam != ra)
  
```

If information for !study_area was not available for a certain data layer, it was often gapfilled using an average of other values within its georegion. Georegions are defined by the United Nations ([unstats.un.org/unsd/methods/m49/m49regin.htm](http://unstats.un.org/unsd/methods/m49/m49regin.htm)). The other countries within the georegion with !study_area are: `r g_rgns$rgn_nam`.  

***layers-empty_swapping-global-mean.csv*** is a list of data layers that did not have values for !study_area and were not able to be gapfilled georegionally. This is because calculated scores of other nearby countries were used to gapfill values for !study_area instead of gapfilling occurring at the regional level. These layers especially should be substituted with local data. 


## *conf* folder
The `conf` folder includes includes R functions (*config.R* and *functions.R*) and *.csv* files containing information that will be accessed by the R functions (*goals.csv*, *pressures_matrix.R*, *resilience_matrix.csv*, and *resilience_weights.csv*).


### *config.r*
`config.r` is an R script that configures labeling and constants appropriately.

### *functions.r*
`functions.r` contains functions for each goal and sub-goal model, which calculate the status and trend using data layers identified as ‘layers’ in `layers.csv`. 

### *goals.csv* 
`goals.csv` is a list of goals and sub-goals and their weights used to calculate the final score for each goal. Other information includes the goal description that is also presented in the Toolbox App. `goals.csv` also indicates the arguments passed to functions.R. These are indicated by two columns: *preindex_function* (functions for all goals that do not have sub-goals, and functions for all sub-goals) and *postindex_function* (functions for goals with sub-goals).  

### *pressures_matrix.csv*
`pressures_matrix.csv` describes the layers (‘layers’ column in layers.csv) needed to calculate pressure categories. The matrix has weights assigned that were determined by Halpern et al. 2012 (Nature) based on scientific literature and expert opinion.

### *resilience_matrix.csv*
`resilience_matrix.csv` describes the layers (‘layers’ column in layers.csv) needed to calculate resilience categories.

### *resilience_weights.csv*
`resilience_weights.csv` describes the weight of various resilience layers, were determined by Halpern et al. 2012 (Nature) based on scientific literature and expert opinion.

## spatial folder 
The spatial folder contains two files: *regions_gcs.js* and *regions_gcs.geojson*. These are spatial files, one in JSON format and one in GeoJSON format. Both are maps displaying the appropriate study area and regions for the assessment. It is possible to view the regions on GitHub, which is able to render the GeoJSON format. Go to this url: [github.com/OHI-Science/!repo/blob/master/subcountry2014/spatial/regions_gcs.geojson](https://github.com/OHI-Science/!repo/blob/master/subcountry2014/spatial/regions_gcs.geojson).

## *launch_app_code.R*
Running `launch_app_code.r` from within the `subcountry2014` folder will launch the Toolbox Application, which will be displayed in a web browser. The Toolbox App will display all input data from the `layers` folder as well as the calculated scores from `scores.csv`.

## *calculate_scores.r*
You will run `calculate_scores.r` when you are ready to calculate scores with your local data and goal models. `calculate_scores.r` calls other functions within the Toolbox to calculate goal scores using the *.csv* files in the *layers* folder that are registered in *layers.csv* and the configurations identified in *config.r*. Scores will be saved in *scores.csv*.

## scores.csv
`scores.csv` reports the calculated scores for the assessment. Scores are reported for each dimension (future, pressures, resilience, score, status, trend) for each reporting region. The scores here were calculated using the data in the repository (extracted from the global assessment) simply to demonstrate the Toolbox has functioned properly. Note that in `scores.csv` there are `!x + 1` region identifiers (*rgn_id*). The combined score for the !study_area is reported in *rgn_id* 0. 





