# prep_bhi.Rmd
create baltic repo. See Issue #407: https://github.com/OHI-Science/issues/issues/407

NOTE: This script superceded `prep_bhi.r`, which originally created the BHI WebApp in April 2015 with PLC Basin *Inters_BALTIC_EEZ_PLC1* regions. `prep_bhi.rmd` here recreates the BHI WebApp in August 2015 with HOLAS Basin *Intersect_HELCOMsubbasins_BALTIC_EEZ_excl_small_poly* regions. 

# Overview
Not all steps were necessary to run this time around. Steps below that were run: Setup, 1, 7. However, I've got the evals off of all of these at the moment (ie, `{r, eval=F}) so it doesn't run now when I don't want it to. 


## 1. setup
```{r setup, eval=F}

# libraries
library(dplyr)
library(tidyr)
library(readr)
library(stringr)
library(rgdal)
library(raster)

# directories
dir_neptune = c('Windows' = '//neptune.nceas.ucsb.edu/data_edit',
                'Darwin'  = '/Volumes/data_edit',
                'Linux'   = '/var/data/ohi')[[ Sys.info()[['sysname']] ]]
dir_custom_bhi = '~/github/ohi-webapps/custom/bhi'
dir_tmp_baltic = file.path(dir_custom_bhi, 'tmp_bhi_contents')

# setwd
setwd('~/github/ohi-webapps')

# variables 
bhi_sc = read_csv('custom/bhi/sc_studies_custom_bhi.csv'); head(bhi_sc)
ind_bhi = str_detect(bhi_sc$sc_key, 'bhi-')
bhi_rgn = bhi_sc$sc_key[ind_bhi]; bhi_rgn
# "bhi-swe" "bhi-fin" "bhi-dnk" "bhi-deu" "bhi-est" "bhi-pol" "bhi-lva" "bhi-ltu" "bhi-rus"

# read in lookup table --if doesn't exist must run Chunk 1: view map
lkp_baltic = read_csv(file.path(dir_custom_bhi, 'baltic_rgns_to_bhi_rgns_lookup_holas.csv')); lkp_baltic


```


## 1. view map and accompanying data; save with ohi data frame 

NOTE: `read_OGR` didn't take care of the **orphan hole** problems in the `Intersect_HELCOMsubbasins_BALTIC_EEZ_Eliminate` shp files provided by the Baltic group. But `readShapePoly` did, providing we set the coordinate reference system (CRS), which I took directly from the output that `read_OGR` gave.

```{r view map, eval=F}

# logicals for if statements below
view_shp = F
clean_spatial = F 
redo_shp = F 


# read in shp files and save with desired headers in data frame. readOGR includes a CRS but doesn't fix orphan holes
bhi_tmp = readOGR(dsn = file.path(dir_neptune, 'git-annex/clip-n-ship/bhi/spatial/custom/raw'),
              layer = 'Intersect_HELCOMsubbasins_BALTIC_EEZ_Eliminate')
# bhi_tmp
# class       : SpatialPolygonsDataFrame 
# features    : 42 
# extent      : 4210802, 5437429, 3404119, 4812329  (xmin, xmax, ymin, ymax)
# coord. ref. : +proj=laea +lat_0=52 +lon_0=10 +x_0=4321000 +y_0=3210000 +ellps=GRS80 +units=m +no_defs 
# variables   : 15
# names       : FID_HELCOM, SB_Code,                  Name, AreaKM2, HELCOM_ID,  Shape_STAr, Shape_STLe, FID_BALTIC, OBJECTID, ID,  Name_1, Shape_Leng, Shape_Le_1, Shape_Area,        Area 
# min values  :          0,       1,             Åland Sea,    1208,   SEA-001,  1207968326,   392729.5,          0,        0,  1, Denmark,   483.7242,    0.00000,    6121.55,    98.62089 
# max values  :         16,      17, Western Gotland Basin,   75093,   SEA-017, 75093468124, 20986555.1,          8,        4,  9,  Sweden,  7113.7737,   90.77792,  160638.70, 31239.66735 

# # readShapePoly doesn't include a coordinate ref system (must set it) but also removes orphan holes
bhi = readShapePoly(file.path(dir_neptune, 'git-annex/clip-n-ship/bhi/spatial/custom/raw',
                   'Intersect_HELCOMsubbasins_BALTIC_EEZ_Eliminate.shp'), 
                  proj4string=CRS(bhi_tmp@proj4string@projargs) # CRS set from bhi_tmp above
bhi_orig = bhi # to archive

# viewing takes a long time
if (view_shp) plot(bhi)

# check for errors in shp file: 'orphaned hole' error encountered in Step 9 below 
if (clean_spatial) source('~/github/ohi-webapps/custom/bhi/clean_spatial_bhi.r') # will overwrite bhi with cleaned file; be sure the last line is uncommented


if (redo_shp) {
  bhi@data # view data
  bhi@data = bhi@data %>%
    mutate(rgn_id = 1:42) %>%
    dplyr::select(rgn_id,
                  area_km2 = Area,
                  cntry_name = Name_1,
                  basin_name = Name) %>%
    mutate(basin_name = str_replace_all(basin_name, '\xc5land Sea', 'Aland Sea'),
           rgn_name = paste(substr(cntry_name, 1, 3), # create rgn_name as eez - basin (eg 'Est - Gulf of Riga')
                            '-',
                            basin_name), sep=' ') %>%
    dplyr::select(rgn_id, area_km2, cntry_name, basin_name, rgn_name) # since 'sep' column exists
  
  
  # save as shapefiles
  writeOGR(bhi, dsn = file.path(dir_neptune, 'git-annex/clip-n-ship/bhi/spatial/custom'), 
           layer = 'baltic_shp', driver = 'ESRI Shapefile', overwrite=T) # will create 4 files: .dbf, .prj, .shp, .shx
  
  
  # create lookup table with unique rgn_ids
  baltic_rgns = bhi@data %>%
    left_join(bhi_sc %>%
                dplyr::select(sc_key, 
                              cntry_name = gl_rgn_name, 
                              gl_rgn_key), 
              by='cntry_name') %>%
    mutate(baltic_rgn_key = tolower(gl_rgn_key)) %>%
    dplyr::select(-gl_rgn_key) %>%
    group_by(cntry_name) %>%
    mutate(sc_id = 1:n()); head(baltic_rgns)
  
  write_csv(baltic_rgns, 'custom/bhi/baltic_rgns_to_bhi_rgns_lookup_holas.csv')
  
}

```

## 2. add all Baltic countries to custom/bhi/sc_studies_custom_bhi.csv by hand
Note: this had already been done previously with `prep_bhi.r`

## 3. create directories in github/clip-n-ship 
Note: this had already been done previously with `prep_bhi.r`

```{r create bhi-xxx dirs, eval=F}

redo_dirs = F

if(redo_dirs) sapply(sprintf('~/github/clip-n-ship/%s', bhi_rgn), dir.create)

```

## 4. create directories in git-annex/clip-n-ship and copy required files for populate_draft_branch()
Note: this had already been done previously with `prep_bhi.r`

```{r populate bhi-xxx dirs, eval=F}

redo_bhi_dirs = F

if (redo_bhi_dirs) {
  # first create the directories
  sapply(sprintf(file.path(dir_neptune, 'git-annex/clip-n-ship/%s'), bhi_rgn), dir.create)
  sapply(sprintf(file.path(dir_neptune, 'git-annex/clip-n-ship/%s/spatial'), bhi_rgn), dir.create)
  sapply(sprintf(file.path(dir_neptune, 'git-annex/clip-n-ship/%s/layers'), bhi_rgn), dir.create)
  
  # for each bhi_rgn
  for (b in bhi_rgn) { # b = 'bhi-rus'
    
    # copy the spatial files
    dir_in  = sprintf(file.path(dir_neptune, 'git-annex/clip-n-ship/%s/spatial'), str_replace(b, 'bhi-', ''))
    dir_out = sprintf(file.path(dir_neptune, 'git-annex/clip-n-ship/%s/spatial'), b)
    
    f_gcs = extension(list.files(dir_in, pattern = 'rgn_offshore_gcs'))
    
    for (f in f_gcs) {
      file.copy(sprintf(file.path(dir_neptune, 'git-annex/clip-n-ship/%s/spatial/rgn_offshore_gcs%s'), str_replace(b, 'bhi-', ''), f),
                sprintf(file.path(dir_neptune, 'git-annex/clip-n-ship/%s/spatial/rgn_offshore_gcs%s'), b, f), overwrite=T)
    }
    
    # copy rgn_offshore_data.csv
    file.copy(sprintf(file.path(dir_neptune, 'git-annex/clip-n-ship/%s/spatial/rgn_offshore_data.csv'), str_replace(b, 'bhi-', '')),
              sprintf(file.path(dir_neptune, 'git-annex/clip-n-ship/%s/spatial/rgn_offshore_data.csv'), b), overwrite=T)
    
    # copy mar_coastalpopn_inland25km_lyr.csv
    file.copy(sprintf(file.path(dir_neptune, 'git-annex/clip-n-ship/%s/layers/mar_coastalpopn_inland25km_lyr.csv'), str_replace(b, 'bhi-', '')),
              sprintf(file.path(dir_neptune, 'git-annex/clip-n-ship/%s/layers/mar_coastalpopn_inland25km_lyr.csv'), b), overwrite=T)
    
  }  
}
```

## 5. run ohi-webapps/create_all.r through populate_draft_branch()
Note: this had already been done previously with `prep_bhi.r`

Also, when run previously with `prep_bhi.r`, problems with `create_gh_repo`; must set `repo_exists = F`

```{r run create_all.r, eval=F, echo=FALSE}
# blank chunk just so chunk and step numbering stay consistent
```


## 6. create bhi repo
Note: this had already been done previously with `prep_bhi.r`

```{r create bhi repo, eval=F}
redo_bhirepo = F

if (redo_bhirepo) {
  dir_bhi = file.path(dir_repos, 'bhi')
  
  # file.copy(list.dirs(file.path(dir_repos, 'bhi-deu')), # Apr 17 this was giving an error; I copied by hand
  #           dir_bhi) 
  
  # rename .Rproj
  file.rename(file.path(dir_bhi, 'bhi-deu.Rproj'),
              file.path(dir_bhi, 'bhi.Rproj'))
  
  # rename scenario folder
  # by hand for the moment
  }
```

## 7. bhi layers: bind possible layers for each bhi-xxx

Rerun August 2015 with new HOLAS BHI regions. 

```{r bhi layers: bind from bhi-xxx repos, eval=F}

# clone existing bhi repo
key = 'bhi'
setwd(dir_repos)
source(sprintf('%s/ohi-webapps/create_init_sc.R', dir_github))

setwd(dir_repos)
unlink(dir_repo, recursive=T, force=T)
repo = clone(git_url, normalizePath(dir_repo, mustWork=F))

# unlink problem layers: 
tounlink = c('lsp_prot_area_inland1km_gl2014.csv',         # lsp layers dealt with separately in step 8 below
             'lsp_prot_area_offshore3nm_gl2014.csv',
             'lsp_prot_area_inland1km_placeholder.csv',    # delete the placeholders to rerun
             'lsp_prot_area_offshore3nm_placeholder.csv',
             'cw_nu_status.csv',                           # delete BHI test layers
             'cw_nu_trend.csv')
for (f in tounlink) unlink(file.path(dir_repos, 'bhi/baltic2015/layers', f), recursive=T, force=T)

# list all layers to copy to bhi repo
lyrs_list = list.files(file.path(dir_repos, 'bhi/baltic2015/layers'), glob2rx('*.csv'), full.names=T) 


# loop through all layers and then all bhi-xxx repos to create appropriate # of regions per layer
for (f in lyrs_list){ # f = "~/github/clip-n-ship/bhi/baltic2015/layers/ao_access_gl2014.csv" 
  
  cat(sprintf('processing %s ... \n', basename(f)))
  
  # read in layer, save names, delete all but headers (a bit hacky this way)
  lyr_tmp = read_csv(f)
  lyr_col = names(lyr_tmp)
  
  # only works for rgn_ids; FIS layers different
  if ('rgn_id' %in% lyr_col){
    
    # delete all data in layer
    lyr_bind = lyr_tmp %>%
      filter(rgn_id == 0)
    
    
    # for every b repo in bhi_rgn list
    for (b in bhi_rgn) { # b = 'bhi-deu'  # could rename this as key (confusing?)
      
      key = b
      source('~/github/ohi-webapps/create_init_sc.r')
      default_scenario = 'region2015'
      
      # read in b's layer
      s = read_csv(file.path(dir_repo, default_scenario, 'layers', basename(f)))
      
      # make sure classes are correct; was a problem for ico_spp_extinction_status_gl2014.csv. 
      # See http://stackoverflow.com/questions/27361081/r-assign-or-copy-column-classes-from-a-data-frame-to-another
      s[] = mapply(FUN = as, s, sapply(lyr_tmp, class), SIMPLIFY=F)
      
      # filter baltic lookp for b
      lkp_b = lkp_baltic %>%
        filter(sc_key == b)
      
      if ('area_km2' %in% lyr_col) s = s %>% select(-area_km2) # use area_km2 from lkp_b (regions) not s (nations)
      if ('rgn_name' %in% lyr_col) s = s %>% select(-rgn_name) # use rgn_name from lkp_b (regions) not s (nations)
      
      # join lookup with layer and select original columns using non-standard evaluation, ie dplyr::*_()
      t = s %>%
        rename(sc_id = rgn_id) %>%
        right_join(lkp_b, by='sc_id') %>%
        select_(.dots = lyr_col)
      
      # bind all together
      lyr_bind = bind_rows(lyr_bind, t)  
      
      }
    
    # save file
    lyr_save = lyr_bind %>%
      arrange(rgn_id)
    
    write_csv(lyr_save, f)
    
    } else {
      cat(sprintf('layer does not have rgn_id variable, do separately: %s', f))
      # "/Users/jstewart/github/clip-n-ship/bhi/baltic2015/layers/fis_b_bmsy_gl2014.csv"
      # "/Users/jstewart/github/clip-n-ship/bhi/baltic2015/layers/fis_meancatch_gl2014.csv"
      # "/Users/jstewart/github/clip-n-ship/bhi/baltic2015/layers/mar_harvest_species_gl2014.csv"
      }
}

```
 
## 8. bhi layers: handle problem layers 

Handle several problem layers individually 

```{r bhi_layers: handle individuals, eval=FALSE}

# recreate rgn_global_gl2014.csv
lkp_baltic %>% select(rgn_id, label = rgn_name) %>%
  write_csv(file.path(dir_repos, 'bhi/baltic2015/layers/rgn_global_gl2014.csv'))


# recreate rgn_labels.csv 
lkp_baltic %>% mutate(type = 'eez', 
                      label = paste(str_extract(cntry_name, pattern='[A-Z][a-z][a-z]'),
                       basin_name, sep = ' - ')) %>%
  select(rgn_id, type, label) %>%
  write_csv(file.path(dir_repos, 'bhi/baltic2015/layers/rgn_labels.csv'))


# recreate rgn_area_sc2014-area.csv
lkp_baltic %>% select(rgn_id, rgn_name, area_km2) %>%
  write_csv(file.path(dir_repos, 'bhi/baltic2015/layers/rgn_area_sc2014-area.csv'))


# recreate rgn_area_inland1km_gl2014.csv and rgn_area_offshore3nm_gl2014.csv
tmp = lkp_baltic %>%
  select(rgn_id) %>%
  mutate(area_km2 = 5) # placeholder
write_csv(tmp, file.path(dir_repos, 'bhi/baltic2015/layers/rgn_area_inland1km_gl2014.csv'))
write_csv(tmp, file.path(dir_repos, 'bhi/baltic2015/layers/rgn_area_offshore3nm_gl2014.csv'))


# recreate lsp_prot_area_inland1km_gl2014.csv and lsp_prot_area_offshore3nm_gl2014.csv
tmp_yrs = 2010:2015
tmp = data.frame(rgn_id = rep(1:dim(lkp_baltic)[1], length(tmp_yrs))) %>%
  arrange(rgn_id) %>%
  mutate(year = rep(tmp_yrs, dim(lkp_baltic)[1]), 
         area_km2 = 10)
write_csv(tmp, file.path(dir_repos, 'bhi/baltic2015/layers', 'lsp_prot_area_inland1km_placeholder.csv'))
write_csv(tmp, file.path(dir_repos, 'bhi/baltic2015/layers', 'lsp_prot_area_offshore3nm_placeholder.csv'))


# recreate rgn_georegions_gl2014.csv very hacky 
tmp = read_csv(file.path(dir_repos, 'bhi/baltic2015/layers/rgn_georegions_gl2014.csv')) %>%
  select(-rgn_id) %>%
  distinct()
tmp2 = bind_rows(
  data.frame(rgn_id = 1:dim(lkp_baltic)[1]) %>%
    mutate(level = tmp$level[1]) %>%
    mutate(georgn_id = tmp$georgn_id[1]), 
  data.frame(rgn_id = 1:dim(lkp_baltic)[1]) %>%
    mutate(level = tmp$level[2]) %>%
    mutate(georgn_id = tmp$georgn_id[2]),
  data.frame(rgn_id = 1:dim(lkp_baltic)[1]) %>%
    mutate(level = tmp$level[3]) %>%
    mutate(georgn_id = tmp$georgn_id[3]))
write_csv(tmp2, file.path(dir_repos, 'bhi/baltic2015/layers/rgn_georegions_gl2014.csv'))


# recreate rgn_georegion_labels_gl2014.csv
tmp = read_csv(file.path(dir_repos, 'bhi/baltic2015/layers/rgn_georegion_labels_gl2014.csv')) %>%
  select(-rgn_id) %>%
  distinct()
tmp2 = bind_rows(
  data.frame(rgn_id = 1:dim(lkp_baltic)[1]) %>%
    mutate(level = tmp$level[1]) %>%
    mutate(label = tmp$label[1]), 
  data.frame(rgn_id = 1:dim(lkp_baltic)[1]) %>%
    mutate(level = tmp$level[2]) %>%
    mutate(label = tmp$label[2]),
  data.frame(rgn_id = 1:dim(lkp_baltic)[1]) %>%
    mutate(level = tmp$level[3]) %>%
    mutate(label = tmp$label[3]))
write_csv(tmp2, file.path(dir_repos, 'bhi/baltic2015/layers/rgn_georegion_labels_gl2014.csv'))


# overwrite np_harvest_product_weight_gl2014.csv layer; update layers.csv 
# see https://github.com/OHI-Science/issues/issues/407#issuecomment-96237694
tmp_prod = c('fish_oil', 'ornamentals', 'seaweeds', 'shells', 'sponges')
data.frame(rgn_id = rep(1:dim(lkp_baltic)[1], length(tmp_prod))) %>%
  arrange(rgn_id) %>%
  mutate(product = rep(tmp_prod, dim(lkp_baltic)[1]),
         weight  = 0.2) %>%
  write_csv(file.path(dir_repos, 'bhi/baltic2015/layers', 'np_harvest_product_weight_placeholder.csv'))

l_csv = file.path(dir_repos, 'bhi/baltic2015/layers.csv')
readLines(l_csv, warn=F, encoding='UTF-8') %>%
  str_replace("np_harvest_product_weight_gl2014.csv", 
              "np_harvest_product_weight_placeholder.csv") %>%
  writeLines(l_csv)


# create dummy cs_nu_status and cs_nu_trend files
data.frame(rgn_id  = 1:dim(lkp_baltic)[1], 
           score = rep(0.5, dim(lkp_baltic)[1])) %>%
  write_csv(file.path(dir_repos, 'bhi/baltic2015/layers', 'cw_nu_status_placeholder.csv'))

data.frame(rgn_id  = 1:dim(lkp_baltic)[1], 
           score = rep(0, dim(lkp_baltic)[1])) %>%
  write_csv(file.path(dir_repos, 'bhi/baltic2015/layers', 'cw_nu_trend_placeholder.csv'))

# and update layers.csv
l_csv = file.path(dir_repos, 'bhi/baltic2015/layers.csv')
readLines(l_csv, warn=F, encoding='UTF-8') %>%
  str_replace("cw_nu_status.csv", 
              "cw_nu_status_placeholder.csv") %>%
   str_replace("cw_nu_trend.csv", 
              "cw_nu_trend_placeholder.csv") %>%
  writeLines(l_csv)

```


## 9. copy whole bhi directory to a tmp location 
important because it will be overwritten in its current location

```{r copy bhi dir, eval=FALSE}

# copy whole bhi directory to a tmp location because it will be overwritten
# cp command: `cp -r from to`. the -r means 'including subdirectories'. The `/.` means contents only, not folder itself

system(sprintf("cp -r %s %s", file.path(dir_repos, 'bhi'), dir_tmp_baltic)) 

# save dated archive too
dir_archive = file.path(dir_tmp_baltic, sprintf('archive/%s', Sys.Date())) #dir.create(dir_archive)
system(sprintf("cp -r %s %s", file.path(dir_repos, 'bhi'), dir_archive)) 

```

## 10. run custom_maps()

proceed with create_all.r: 

- `custom_maps()`

```{r run custom_maps, eval=FALSE}

keys_redo = 'bhi'
key = keys_redo[1]

setwd(dir_repos)
source(sprintf('%s/ohi-webapps/create_init_sc.R', dir_github))
setwd(dir_repo)

# fun custom_maps
custom_maps(key) # if orphaned hole, read in original shp file with readShapePoly and run cleangeo rather than readOGR

```

## 11. populate_draft_branch() delete repo

Only run the first part of populate_draft_branch()

- `populate_draft_branch()`

```{r populate_draft_branch delete repo, eval=FALSE}

# key setup

key = 'bhi'
setwd(dir_repos)
source(sprintf('%s/ohi-webapps/create_init_sc.R', dir_github))
setwd(dir_repo)


## first chunk of `populate_draft_branch(): clone and delete existing repo; ~L270 ----
wd = getwd()
library(rgdal)

# clone repo
setwd(dir_repos)
unlink(dir_repo, recursive=T, force=T)
repo = clone(git_url, normalizePath(dir_repo, mustWork=F))
setwd(dir_repo)

# get remote branches
remote_branches = sapply(branches(repo, 'remote'), function(x) str_split(x@name, '/')[[1]][2])

# initialize
if (length(remote_branches)==0){
  system('touch README.md')
  system('git add -A; git commit -m "first commit"')
  try(system('git remote rm origin')) # added by JSL Mar 13 2015;
  # http://stackoverflow.com/questions/1221840/remote-origin-already-exists-on-git-push-to-new-repository
  system(sprintf('git remote add origin https://github.com/OHI-Science/%s.git', key))
  system('git push -u origin master')
  system('git pull')
  remote_branches = sapply(branches(repo, 'remote'), function(x) str_split(x@name, '/')[[1]][2])
}

# rename if draft & published don't already exist
if (length(setdiff(c('draft','published'), remote_branches)) > 0 & length(remote_branches) > 0){
  rename_branches(key)
  remote_branches = sapply(branches(repo, 'remote'), function(x) str_split(x@name, '/')[[1]][2])
}

# ensure on draft branch ----
checkout(repo, 'draft')

# recreate empty dir, except hidden .git
del_except = ''
for (f in setdiff(list.files(dir_repo, all.files=F), del_except)) unlink(file.path(dir_repo, f), recursive=T, force=T)

```

## 12. paste `bhi` info from steps into bhi repo 

copy existing bhi from Chunks 6-9 into this repo

```{r paste created bhi info into bhi repo, eval=F}


# cp command: `cp -r from to`. the -r means 'including subdirectories'. The `/.` means contents only, not folder itself
 system(sprintf("cp -r %s/%s/. %s", dir_tmp_baltic, 'bhi', file.path(dir_repos, 'bhi')))

```

## 13. populate_draft_branch spatial

overwrite existing json and geojson files with new maps from populate_draft_branch()

```{r populate_draft_branch spatial, eval=F}

key = 'bhi'
setwd(dir_repos)
source(sprintf('%s/ohi-webapps/create_init_sc.R', dir_github))
setwd(dir_repo)

# from populate_draft_branch, ~L333

# spatial
f_js_old      = file.path(dir_annex_sc, 'regions_gcs.js')
f_geojson_old = file.path(dir_annex_sc, 'regions_gcs.geojson')
f_js          = file.path(dir_annex_sc, 'spatial', 'regions_gcs.js')
f_geojson     = file.path(dir_annex_sc, 'spatial', 'regions_gcs.geojson')
if (file.exists(f_js_old)) file.rename(f_js_old, f_js)
if (file.exists(f_geojson_old)) file.rename(f_geojson_old, f_geojson)
txt_shp_error = sprintf('%s/%s_shp_to_geojson.txt', dir_errors, key)
unlink(txt_shp_error)
if (!file.exists(f_js)){                                              
  f_shp = file.path(dir_annex, key, 'spatial', 'rgn_offshore_gcs.shp')
  cat(sprintf('  shp_to_geojson -- %s\n', format(Sys.time(), '%X')))
  v = try(shp_to_geojson(f_shp, f_js, f_geojson))
  if (class(v)=='try-error'){
    cat(as.character(traceback(v)), file=txt_shp_error)
    next
  }
}
for (f in c(f_js, f_geojson)){ # f = f_spatial[1]
  if (key != 'bhi')  file.copy(f, sprintf('spatial/%s', basename(f)), overwrite=T) # original
  if (key == 'bhi') file.copy(f, sprintf('baltic2015/spatial/%s', basename(f)), overwrite=T) # BHI hack
  cat(sprintf('copying from %s', f))
}
 
```

## 13. populate_draft_branch config.r

Overwrite line in config.r that sets map's zoom center 

```{r populate_draft_branch config.r, eval=F}
    
key = 'bhi'
setwd(dir_repos)
source(sprintf('%s/ohi-webapps/create_init_sc.R', dir_github))
setwd(dir_repo)

# filenames
f_in  = file.path(dir_repos, 'bhi', 'baltic2015/conf/config.r')
f_out = f_in 

# from populate_draft_branch ~ L647
s = readLines(f_in, warn=F, encoding='UTF-8') 

# get map centroid and zoom level
# TODO: http://gis.stackexchange.com/questions/76113/dynamically-set-zoom-level-based-on-a-bounding-box
# var regions_group = new L.featureGroup(regions); map.fitBounds(regions_group.getBounds());
p_shp  = file.path(dir_annex_sc, 'spatial', 'rgn_offshore_gcs.shp')
p      = readOGR(dirname(p_shp), tools::file_path_sans_ext(basename(p_shp)))
p_bb   = data.frame(p@bbox) # max of 2.25
p_ctr  = rowMeans(p_bb)
p_zoom = 12 - as.integer(cut(max(transmute(p_bb, range = max - min)), c(0, 0.25, 0.5, 1, 2.5, 5, 10, 20, 40, 80, 160, 320, 360)))

# set map center and zoom level
s = s %>%
  str_replace("map_lat.*", sprintf('map_lat=%g; map_lon=%g; map_zoom=%d', p_ctr['y'], p_ctr['x'], p_zoom))

# use just rgn_labels (not rgn_global)
s = gsub('rgn_global', 'rgn_labels', s)

writeLines(s, f_out)

 
```


## 13. Test bhi's calculate_scores.r

```{r test bhi calculate_scores, eval=F}

setwd(file.path(dir_repos, 'bhi', 'baltic2015'))

# load scenario configuration
conf = Conf('conf')

# run checks on scenario layers
CheckLayers('layers.csv', 'layers', flds_id=conf$config$layers_id_fields)

# load scenario layers
layers = Layers('layers.csv', 'layers')

# calculate scenario scores
scores = CalculateAll(conf, layers, debug=F)
write.csv(scores, 'scores.csv', na='', row.names=F)

```


## 14. Run altered create_all fxns

Run these with `ohi-functions.r`, not `ohi-travis-functions.r`

- push repo back to github
- no need to overwrite `.travis.yml` since based on existing `bhi` repo


```{r create_all push etc, eval=F}

key = 'bhi'
setwd(dir_repos)
source(sprintf('%s/ohi-webapps/create_init_sc.R', dir_github))
source(sprintf('%s/ohi-webapps/ohi-functions.r', dir_github)) 
setwd(dir_repo)


# run the following:

# push draft branch ~ adapted from create.all
setwd(dir_repo)
push_branch('draft') # source('ohi-functions.r')
system('git pull')

# calculate scores ~~ adapted from create.all
setwd(dir_repo)
calculate_scores_notravis() # JSL ERRORING ON ECO

# create flower plot and table
setwd(dir_repo)
update_results()

# push draft and published branches --h
setwd(dir_repo)
push_branch('draft')
merge_published_draft(key) # from create_functions
  ## error fixes here because of merge conflict with layers.csv
  # Manually fixed head issues in layers.csv (published branch)
  # system('git status') # which branch am I on?
  # system('git add -A layers.csv')
  # system('git commit -m "fixed merge prob in layers.csv" ')
  # system('git push')
  # system('git pull')
system('git checkout draft')


# don't need to run create_functions.r - populate_website()

# from ohi-functions.r --not create_functions.r - create_pages() 
# create pages based on results
setwd(dir_repo)
system('git pull; git checkout draft; git pull')
update_pages()
system('git checkout gh-pages; git pull; git checkout published; git pull')

deploy_app_nceas(key, nceas_user)

```

`