# this is prep_arc.Rmd
create arctic repo. See Issue #516: https://github.com/OHI-Science/issues/issues/516
sins_BALTIC_EEZ_excl_small_poly* regions. 

# Overview
I've got the evals off of all of these at the moment (ie, `{r, eval=F}) so it doesn't run now when I don't want it to. 


## 1. setup
```{r setup, eval=F}


library(dplyr)
library(readr)
library(stringr)
library(rgdal)
library(raster)
library(rgeos)
library(maptools)

dir_neptune = c('Windows' = '//neptune.nceas.ucsb.edu/data_edit',
                'Darwin'  = '/Volumes/data_edit',
                'Linux'   = '/var/data/ohi')[[ Sys.info()[['sysname']] ]]

setwd('~/github/ohi-webapps')
source('create_init.R')
source('create_functions.R')

arc_cntrys = c('rus', 'can', 'usa', 'nor', 'grl')

```


## 1. view map and accompanying data; save with ohi data frame 

NOTE: see `custom/bhi/prep_bhi.rmd` for reasoning behind using `readShapePoly` instead of `read_OGR`.

```{r view map, eval=F}

# logicals for if statements below
clean_spatial = F 
redo_shp = F 


# read in shp files and save with desired headers in data frame. 

# without bering strait
arc_raw = readOGR(dsn = file.path(dir_neptune, 'git-annex/clip-n-ship/arc/spatial/custom/raw'),
              layer = 'pan_arctic_boundaries'); arc_raw  # also tried panarctic_region but had lat/lon

arc = spTransform(arc_raw, CRS('+init=epsg:4326')); arc   # spatialreference.org/ref/epsg/4326/
projection(arc)<- "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0 "


# with bering strait
arc_bsr_raw = readOGR(dsn = file.path(dir_neptune, 'git-annex/clip-n-ship/arc/spatial/custom/raw'),
              layer = 'panarctic_plus_bsr_region'); arc_bsr_raw

arc_bsr = spTransform(arc_bsr_raw, CRS('+init=epsg:4326')); arc_bsr   # spatialreference.org/ref/epsg/4326/
plot(arc_bsr)


```


## Create shape file of combined 5 Arctic Countries 

This takes awhile. Must read in each separately (there is a way to loop it without saving interum files, maybe that would be better). but then can save as one. 

```{r create shape file of binded arctic countries, eval=F}

# setup 
arc_cntrys = c('usa', 'can', 'nor', 'rus', 'grl')
dir_cns = file.path(sprintf('%s/git-annex/clip-n-ship/%s/spatial', dir_neptune, arc_cntrys)) %>% setNames(arc_cntrys)
dir_arc = file.path(dir_neptune, 'git-annex/clip-n-ship/arc/spatial/custom/intermediate')
arctic_extent = extent(-180, 180, 66.5628, 90)
sp_layer = 'rgn_offshore_gcs'

# usa
sp_usa = readOGR(as.character(dir_cns['usa']), sp_layer)
sp_usa@data = sp_usa@data %>% dplyr::select(rgn_id, rgn_name, area_km2, Shape_Leng, Shape_Area)
sp_usa_crop = crop(sp_usa, arctic_extent)
writeOGR(sp_usa_crop, dsn=dir_arc, layer='sp_usa_crop', driver='ESRI Shapefile', overwrite=T) 

# can
sp_can = readOGR(as.character(dir_cns['can']), sp_layer)
sp_can@data = sp_can@data %>% dplyr::select(rgn_id, rgn_name, area_km2, Shape_Leng, Shape_Area)
sp_can_crop = crop(sp_can, arctic_extent)
writeOGR(sp_can_crop, dsn=dir_arc, layer='sp_can_crop', driver='ESRI Shapefile', overwrite=T) 

# nor
sp_nor = readOGR(as.character(dir_cns['nor']), sp_layer)
sp_nor@data = sp_nor@data %>% dplyr::select(rgn_id, rgn_name, area_km2, Shape_Leng, Shape_Area)
sp_nor_crop = crop(sp_nor, arctic_extent)
writeOGR(sp_nor_crop, dsn=dir_arc, layer='sp_nor_crop', driver='ESRI Shapefile', overwrite=T) 

# rus
sp_rus = readOGR(as.character(dir_cns['rus']), sp_layer)
sp_rus@data = sp_rus@data %>% dplyr::select(rgn_id, rgn_name, area_km2, Shape_Leng, Shape_Area)
sp_rus_crop = crop(sp_rus, arctic_extent)
writeOGR(sp_rus_crop, dsn=dir_arc, layer='sp_rus_crop', driver='ESRI Shapefile', overwrite=T) 

# grl
sp_grl = readOGR(as.character(dir_cns['grl']), sp_layer)

sp_grl@data = sp_grl@data %>% dplyr::select(rgn_id, rgn_name, area_km2, Shape_Leng, Shape_Area)
sp_grl_crop = crop(sp_grl, arctic_extent)
writeOGR(sp_grl_crop, dsn=dir_arc, layer='sp_grl_crop', driver='ESRI Shapefile', overwrite=T) 

 # save as shapefiles
  

# bind together
#borrowing from gis.stackexchange.com/questions/32732/proper-way-to-rbind-spatialpolygonsdataframes-with-identical-polygon-ids

datanames = c('sp_usa_crop', 'sp_can_crop', 'sp_nor_crop', 'sp_rus_crop', 'sp_grl_crop')
data(list = datanames)
lst = lapply(datanames,get)

# example: to get all ID's (since there will be repeats otherwise)
sapply(slot(sp_usa_crop, "polygons"), function(x) slot(x, "ID"))


#To make them uniform we can write a function using the spChFIDs function from sp:
makeUniform<-function(SPDF){
  pref<-substitute(SPDF)  #just putting the file name in front.
  newSPDF<-spChFIDs(SPDF,as.character(paste(pref,rownames(as(SPDF,"data.frame")),sep="_")))
  return(newSPDF)
}

#now to do this for all our country files
newIDs<-lapply(lst,function(x) makeUniform(x))

#back to your code...
arctic <- do.call( rbind, newIDs )


# 
# # just testing
# sp_usa_crop@data = sp_usa_crop@data %>% dplyr::select(rgn_id, rgn_name, area_km2, Shape_Leng, Shape_Area)
# sp_nor_crop@data = sp_nor_crop@data %>% dplyr::select(rgn_id, rgn_name, area_km2, Shape_Leng, Shape_Area)
# 
# sp_arc = spRbind(sp_usa_crop, sp_nor_crop, sp_can_crop)
# sp_arc@data = sp_arc@data %>% mutate(arc_id = 1:6)
# sp_can_crop@data %>% mutate(arc_id = 1:3)
# sp_arc = spRbind(sp_arc, sp_can_crop)


```


## 



## Create Arctic Lookup Table
arc_cntrys regions to arctic regions

```{r create lookup, eval=F}

# create lookup table similar to baltic_rgns_to_bhi_rgns_lookup.csv

```



```{r, eval=F}


#CONTINUE FROM HERE --COPIED FROM prep_bhi.rmd

# check for errors in shp file: 'orphaned hole' error encountered in Step 9 below 
# if (clean_spatial) source('~/github/ohi-webapps/custom/bhi/clean_spatial_bhi.r') # will overwrite bhi with cleaned file; be sure the last line is uncommented
# 
# 
# if (redo_shp) {
#   bhi@data # view data
#   bhi@data = bhi@data %>%
#     mutate(rgn_id = 1:42) %>%
#     dplyr::select(rgn_id,
#                   area_km2 = Area,
#                   cntry_name = Name_1,
#                   basin_name = Name) %>%
#     mutate(basin_name = str_replace_all(basin_name, '\xc5land Sea', 'Aland Sea'),
#            rgn_name = paste(substr(cntry_name, 1, 3), # create rgn_name as eez - basin (eg 'Est - Gulf of Riga')
#                             '-',
#                             basin_name), sep=' ') %>%
#     dplyr::select(rgn_id, area_km2, cntry_name, basin_name, rgn_name) # since 'sep' column exists
#   
#   
#   # save as shapefiles
#   writeOGR(bhi, dsn = file.path(dir_neptune, 'git-annex/clip-n-ship/bhi/spatial/custom'), 
#            layer = 'baltic_shp', driver = 'ESRI Shapefile', overwrite=T) # will create 4 files: .dbf, .prj, .shp, .shx
#   
#   
#   # create lookup table with unique rgn_ids
#   bhi_sc = read_csv('custom/bhi/sc_studies_custom_bhi.csv'); head(bhi_sc)
#   
#   baltic_rgns = bhi@data %>%
#     left_join(bhi_sc %>%
#                 dplyr::select(sc_key, 
#                               cntry_name = gl_rgn_name, 
#                               gl_rgn_key), 
#               by='cntry_name') %>%
#     mutate(baltic_rgn_key = tolower(gl_rgn_key)) %>%
#     dplyr::select(-gl_rgn_key) %>%
#     group_by(cntry_name) %>%
#     mutate(sc_id = 1:n()); head(baltic_rgns)
#   
#   write_csv(baltic_rgns, 'custom/bhi/baltic_rgns_to_bhi_rgns_lookup_holas.csv')
#   
}

```