# this is prep_arc.Rmd
create arctic repo. See Issue #516: https://github.com/OHI-Science/issues/issues/516

# Overview
I've got the evals off of all of these at the moment (ie, `{r, eval=F}) so it doesn't run now when I don't want it to. 

- called from `ohi-webapps/edit_webapps.rmd`
- using spatial files from existing OHI+ repos for 5 Arctic countries, clip to Arctic circle and save
- bind these together
- using these regions for the Arctic repo `arc`, create populate draft branch.


## 1. setup

```{r setup, eval=F}

# libraries
library(dplyr)
library(readr)
library(stringr)
library(rgdal)
library(raster)
library(rgeos)
library(maptools)

# directories and source files
dir_neptune = c('Windows' = '//neptune.nceas.ucsb.edu/data_edit',
                'Darwin'  = '/Volumes/data_edit',
                'Linux'   = '/var/data/ohi')[[ Sys.info()[['sysname']] ]]

setwd('~/github/ohi-webapps')
source('create_init.R')
source('create_functions.R')


# arctic-specific variables 
arc_cntrys = c('usa', 'can', 'nor', 'rus', 'grl')
dir_cns = file.path(sprintf('%s/git-annex/clip-n-ship/%s/spatial', dir_neptune, arc_cntrys)) %>% setNames(arc_cntrys)
dir_arc = file.path(dir_neptune, 'git-annex/clip-n-ship/arc/spatial/custom/intermediate')

```

## 2. Clip to Arctic Circle and save shape files of 5 Arctic Countries 

Run one-time only. Very time-intensive. 

This takes awhile. Must read in each separately (there is a way to loop it without saving interum files, maybe that would be better). but then can save as one. 

```{r clip and save 5 shape files, eval=F}

# to rerun
reclip_resave = F

# setup
arctic_extent = extent(-180, 180, 66.5628, 90)
sp_layer = 'rgn_offshore_gcs'

if (reclip_resave) { 
  
  # read in individual shp files from existing arctic repos and save
  # usa
  sp_usa = readOGR(as.character(dir_cns['usa']), sp_layer)
  sp_usa@data = sp_usa@data %>% dplyr::select(rgn_id, rgn_name, area_km2, Shape_Leng, Shape_Area)
  sp_usa_crop = crop(sp_usa, arctic_extent)
  writeOGR(sp_usa_crop, dsn=dir_arc, layer='sp_usa_crop', driver='ESRI Shapefile', overwrite=T) 
  
  # can
  sp_can = readOGR(as.character(dir_cns['can']), sp_layer)
  sp_can@data = sp_can@data %>% dplyr::select(rgn_id, rgn_name, area_km2, Shape_Leng, Shape_Area)
  sp_can_crop = crop(sp_can, arctic_extent)
  writeOGR(sp_can_crop, dsn=dir_arc, layer='sp_can_crop', driver='ESRI Shapefile', overwrite=T) 
  
  # nor
  sp_nor = readOGR(as.character(dir_cns['nor']), sp_layer)
  sp_nor@data = sp_nor@data %>% dplyr::select(rgn_id, rgn_name, area_km2, Shape_Leng, Shape_Area)
  sp_nor_crop = crop(sp_nor, arctic_extent)
  writeOGR(sp_nor_crop, dsn=dir_arc, layer='sp_nor_crop', driver='ESRI Shapefile', overwrite=T) 
  
  # rus
  sp_rus = readOGR(as.character(dir_cns['rus']), sp_layer)
  sp_rus@data = sp_rus@data %>% dplyr::select(rgn_id, rgn_name, area_km2, Shape_Leng, Shape_Area)
  sp_rus_crop = crop(sp_rus, arctic_extent)
  writeOGR(sp_rus_crop, dsn=dir_arc, layer='sp_rus_crop', driver='ESRI Shapefile', overwrite=T) 
  
  # grl
  sp_grl = readOGR(as.character(dir_cns['grl']), sp_layer)
  sp_grl@data = sp_grl@data %>% dplyr::select(rgn_id, rgn_name, area_km2, Shape_Leng, Shape_Area)
  sp_grl_crop = crop(sp_grl, arctic_extent)
  writeOGR(sp_grl_crop, dsn=dir_arc, layer='sp_grl_crop', driver='ESRI Shapefile', overwrite=T) 
  
} 

```

## 2. Bind and save shape files for 1 Arctic Study Area 

Run one-time only as well, although this doesn't take long to execute.

```{r bind and save arctic shape files, eval=F}

# read in separate sp files
sp_usa_crop = readOGR(dir_arc, 'sp_usa_crop')
sp_can_crop = readOGR(dir_arc, 'sp_can_crop')
sp_nor_crop = readOGR(dir_arc, 'sp_nor_crop')
sp_rus_crop = readOGR(dir_arc, 'sp_rus_crop')
sp_grl_crop = readOGR(dir_arc, 'sp_grl_crop')

# give all unique polygon IDs to be able to rbind and 
# avoid Error in validObject(res) : invalid class “SpatialPolygons” object: non-unique Polygons ID slot values
# https://stat.ethz.ch/pipermail/r-sig-geo/2009-May/005666.html
sp_usa_crop <- spChFIDs(sp_usa_crop, paste("usa", sapply(slot(sp_usa_crop, "polygons"), slot, "ID"), sep="_"))
sp_can_crop <- spChFIDs(sp_can_crop, paste("can", sapply(slot(sp_can_crop, "polygons"), slot, "ID"), sep="_"))
sp_nor_crop <- spChFIDs(sp_nor_crop, paste("nor", sapply(slot(sp_nor_crop, "polygons"), slot, "ID"), sep="_"))
sp_rus_crop <- spChFIDs(sp_rus_crop, paste("rus", sapply(slot(sp_rus_crop, "polygons"), slot, "ID"), sep="_"))
sp_grl_crop <- spChFIDs(sp_grl_crop, paste("grl", sapply(slot(sp_grl_crop, "polygons"), slot, "ID"), sep="_"))


# bind together. rbind allows you to bind multiple; spRbind allows you to bind 2
sp_arc = rbind(sp_usa_crop, sp_can_crop, sp_nor_crop, sp_rus_crop, sp_grl_crop)
plot(sp_arc)
sp_arc@data
sp_arc@data = sp_arc@data %>%
  rename(rgn_id_sc = rgn_id) # %>% # non-unique region ids from original 5 repos
#   mutate(rgn_id = 1:20) %>%
#   select(rgn_id, rgn_id_sc, rgn_name, area_km2)

# save shapefiles
writeOGR(sp_arc, dsn=dir_arc, layer='sp_arc', driver='ESRI Shapefile', overwrite=T) 

```


## Create Arctic Lookup Table
arc_cntrys regions to arctic regions

```{r create lookup, eval=F}

# create lookup table similar to baltic_rgns_to_bhi_rgns_lookup.csv

```



```{r, eval=F}


#CONTINUE FROM HERE --COPIED FROM prep_bhi.rmd

# check for errors in shp file: 'orphaned hole' error encountered in Step 9 below 
# if (clean_spatial) source('~/github/ohi-webapps/custom/bhi/clean_spatial_bhi.r') # will overwrite bhi with cleaned file; be sure the last line is uncommented
# 
# 
# if (redo_shp) {
#   bhi@data # view data
#   bhi@data = bhi@data %>%
#     mutate(rgn_id = 1:42) %>%
#     dplyr::select(rgn_id,
#                   area_km2 = Area,
#                   cntry_name = Name_1,
#                   basin_name = Name) %>%
#     mutate(basin_name = str_replace_all(basin_name, '\xc5land Sea', 'Aland Sea'),
#            rgn_name = paste(substr(cntry_name, 1, 3), # create rgn_name as eez - basin (eg 'Est - Gulf of Riga')
#                             '-',
#                             basin_name), sep=' ') %>%
#     dplyr::select(rgn_id, area_km2, cntry_name, basin_name, rgn_name) # since 'sep' column exists
#   
#   
#   # save as shapefiles
#   writeOGR(bhi, dsn = file.path(dir_neptune, 'git-annex/clip-n-ship/bhi/spatial/custom'), 
#            layer = 'baltic_shp', driver = 'ESRI Shapefile', overwrite=T) # will create 4 files: .dbf, .prj, .shp, .shx
#   
#   
#   # create lookup table with unique rgn_ids
#   bhi_sc = read_csv('custom/bhi/sc_studies_custom_bhi.csv'); head(bhi_sc)
#   
#   baltic_rgns = bhi@data %>%
#     left_join(bhi_sc %>%
#                 dplyr::select(sc_key, 
#                               cntry_name = gl_rgn_name, 
#                               gl_rgn_key), 
#               by='cntry_name') %>%
#     mutate(baltic_rgn_key = tolower(gl_rgn_key)) %>%
#     dplyr::select(-gl_rgn_key) %>%
#     group_by(cntry_name) %>%
#     mutate(sc_id = 1:n()); head(baltic_rgns)
#   
#   write_csv(baltic_rgns, 'custom/bhi/baltic_rgns_to_bhi_rgns_lookup_holas.csv')
#   
}

```